\section{Foundations of (in)security}
\paragraph{What is computer security?}
The protection afforded to an automated information system in order to attain the applicable objectives of preserving the integrity, the availability and confidentiality of information systems resources.

\paragraph{What is confidentiality? Give an example}
Confidentiality assures that a piece of information can be read by those who can read it. Confidentiality can be achieved with authentication.
	
\paragraph{What is integrity? Give an example}
Integrity assures that a piece of information communicates the right thing/concept. It can be achieved by using digital signatures.
	
\paragraph{What is availability? Give an example}
Availability assures that a piece of information can be reached when needed. A good way to achieve availability is to have redundancy for your information systems.
	
\paragraph{What is Thompson's view on compilers?}
The compiler can be modified in any way to include code that never appears in the source code. And depending on how many generations passed, it will not appear in the previous compiler versions source code either!
	
\paragraph{What is a computer network?}
A computer network is a general architecture that allows computer systems to share information remotely.

\paragraph{What is an outright malicious attacker? And where can this attacker appear?}
An outright malicious attacker typically reads or modifies some information, in part or fully. It can appear on a lot of places, for example as a malware infection on your computer, or someone doing a MITM attack on your local network.

\paragraph{What is an honest-but-curious attacker? And where can this attacker appear?}
The goal of this attacker is to use the client's information after correctly handling the service. They can appear for example with a MITM attack on the local network. Another example is a DB server, it provides agreed service correctly. However, after the query is delivered to the client, the server uses the query's information to perform user profiling.